A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-09-14 03_Yield_MetaAnalysis.Rmd
yied > yield

```{r metafor_plot_yied}
results_mv %>%
   filter(Treatment != "control") %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, mu)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `CI_{L}`, ymax = `CI_{U}`)) +
   coord_flip() +
   labs(caption = "Bars indicate 95% confidence intervals")+
   ylab(expression(paste(
      "Mean yield difference to control (t ha" ^ -1, ")", sep = ""
   ))) +
   scale_x_discrete(
      "Moderator variable",
      labels = c(
         expression("Late"["plus"]),
         expression("Late"["single"]),
         expression("Recommended"["plus"]),
         expression("Recommended"["single"]),
         expression("Early"["single"])
      )
   )
ggsave("paper/figures/Fig2_means_difference.png",
       height = 3,
       dpi = 500)
```

>>>>

```{r metafor_plot_yield}
results_mv %>%
   filter(Treatment != "control") %>%
   mutate(Treatment = factor(Treatment, levels = rev(
      c(
         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, mu)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `CI_{L}`, ymax = `CI_{U}`)) +
   coord_flip() +
   labs(caption = "Bars indicate 95% confidence intervals")+
   ylab(expression(paste(
      "Mean yield difference to control (t ha" ^ -1, ")", sep = ""
   ))) +
   scale_x_discrete(
      "Moderator variable",
      labels = c(
         expression("Late"["plus"]),
         expression("Late"["single"]),
         expression("Recommended"["plus"]),
         expression("Recommended"["single"]),
         expression("Early"["single"])
      )
   )
ggsave("paper/figures/Fig2_means_difference.png",
       height = 3,
       dpi = 500)
```
